Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-07-15 content/conclusions.tex
Minor fixes to bibliography, fixed missing citation in conclusion. Minor stylistic tweaks to template.

\begin{nestedsection}{Conclusions}{conclusions}
	We have presented Windowed Continuous Datalog (\emph{WC-Datalog}), a well-founded semantics for continuous reasoning at the expressivity of OWL 2 RL, extended incrementally from that of positive Datalog with temporal annotation, streams and windowing semantics.
	In this way it differs from other temporal interpretations of Datalog \citep{TODO} in that it forgoes the concepts of conventional temporal reasoning, replacing them with the windowing semantics of stream processing, casting a continuous program as a series of discrete states.
	WC-Datalog supports the derivation of sets of facts as the entailment of each discrete state of a continuous program and the derivation of concise streams of facts as the entailment of a continuous program over time, in a similar manner to the \emph{RStream}, \emph{IStream} and \emph{DStream} operators of the CQL continuous query language \citep{CQL}.
	In addition to this, however, it also supports the low-complexity derivation of the entailment of each discrete state from the streamed entailment of the continuous program via the application of windows to the concise streams, leading to the well-founded definition of a \emph{valid window} over the combined streams $P$ and $N$, being the outputs of the reasoning equivalents of the \emph{IStream} and \emph{DStream}.
	Thus WC-Datalog represents a well-founded semantics not only for continuous reasoning, but for coherent and concise streamed entailments of continuous programs, suitable for consumption in further stream processing.

>>>>

\begin{nestedsection}{Conclusions}{conclusions}
	We have presented Windowed Continuous Datalog (\emph{WC-Datalog}), a well-founded semantics for continuous reasoning at the expressivity of OWL 2 RL, extended incrementally from that of positive Datalog with temporal annotation, streams and windowing semantics.
	In this way it differs from other temporal interpretations of Datalog \citep{OrgunWadge92,Tuzhilin93} in that it forgoes the concepts of conventional temporal reasoning, replacing them with the windowing semantics of stream processing and casting a continuous program as a series of discrete states.
	WC-Datalog supports the derivation of sets of facts as the entailment of each discrete state of a continuous program and the derivation of concise streams of facts as the entailment of a continuous program over time, in a similar manner to the \emph{RStream}, \emph{IStream} and \emph{DStream} operators of the CQL continuous query language \citep{CQL}.
	In addition to this, however, it also supports the low-complexity derivation of the entailment of each discrete state from the streamed entailment of the continuous program via the application of windows to the concise streams, leading to the well-founded definition of a \emph{valid window} over the combined streams $P$ and $N$, being the outputs of the reasoning equivalents of the \emph{IStream} and \emph{DStream}.
	Thus WC-Datalog represents a well-founded semantics not only for continuous reasoning, but for coherent and concise streamed entailments of continuous programs, suitable for consumption in further stream processing.
